### 2020-09-17 paper/experiments.tex
Add paragraph on JgraphT

@@

>>>>

\subsubsection{JGraphT implementation}

% \begin{wrapfigure}{r}{0.5\textwidth}
%   \centering\
%   \input{plots/java.java.t.in.out.csv.lines.pgf}
%   \caption{JGraphT Berge recognition performance}
%   \label{plot:jgrapht}
% \end{wrapfigure}
\begin{figure}
  \centering
  \input{plots/java.java.t.in.out.csv.lines.pgf}
  \caption{JGraphT Berge recognition performance}
  \label{plot:jgrapht}
\end{figure}

JGraphT \cite{jgrapht} is an open-source Java library of graph data structures and algorithms. It provides many graph algorithms, such as bipartite and general matchings, flows and colorings. In a research paper about it \cite{jgraphtPaper}, the library is described as a robust and performance-driven graph library. It is used in many commercial and open-source projects, including Apache Cassandra database, Apache Storm and Graal JVM.

The Berge recognition algorithm implemented there is exactly the CCLSV algorithm, but during our tests the performance was much worse when compared to our implementations. See \Cref{plot:jgrapht} for a overall running times on line graphs of random bipartite graphs. After looking at the source code of the Berge recognition algorithm, we think that the poor performance may be caused by the lack of optimizations we talked about in Sections \ref{sec:secnaive} and \ref{sec:Optimizations} -- the implementation is rather straightforward and unoptimized. For example in many places it uses HashSets when arrays would suffice.

@@

All of our implementations are significantly faster than the only other perfect graph recognition implementation we found.

### 2020-09-17 paper/implementation.tex
Add paragraph on JgraphT

\section{Berge graphs recognition: na\"ive approach}
When implementing an algorithm with the running time of $O(|V|^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is at all usable. We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach. So, to test the usability of CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm. Let us describe it briefly.

>>>>

\section{Berge graphs recognition: na\"ive approach}
\label{sec:secnaive}
When implementing an algorithm with the running time of $O(|V|^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is at all usable. We found only one existing attempt at implementing a perfect graph recognition algorithm, but it suffers from a very poor performance (see \Cref{plot:jgrapht}). So, to test the usability of the CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm. Let us describe it briefly.
